Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-14 thesis/chapters/ch_introduction.tex
final edits for the day. DJD is here

%
% 
%
\textbf{Not quite sure if onez models should be its own section:} One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models. This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars. Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g. \cite{FinlatorDave2008,Bouche2010}). The assumptions that go into these models vary dramatically with complexity. Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e. ignoring stellar lifetimes) or that all metals mix instantly and homogenously. More complex models .

Regardless of the assumptions that go into these models, they are powerful tools used

 with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing. While simple, these models have been used extensively to explain the mean evolution of stars in chemical space in individual galaxies.

Mention simulations here somewhere (a la naab and ostriker)

@@

We give a primer on how to model galactic evolution in hydrodynamics simulations. We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this dissertation. This is meant to be a broad overview of the physical processes modelled in such simulations, focusing on aspects of their implementation rather than the derivation of theory behind such processes. While important, the latter is better reserved for a much more detailed work (i.e. textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation. This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars},

But first, we note that Astronomy jargon is full of idiosyncrisies. As metioned before, the word ``chemical" in the ``galactic chemical evolution" is a bit of a misnomer. This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the astrochemistry that those elements may participate in. Likewise, ``metals" refers broadly to every element except H and He. Throughout this dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars. This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that this is impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System. The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}. Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines) and O as a proxy in gas abundances (as it is the most abundant metal in the Universe and has convenient, strong emisson lines). These metallicity proxies are commonly reported in some form of normalized abundance ratio. For stellar metallicities, this is given in the form [A/B], where [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, and $N$ refers to the number of atoms of a given element (usually as [Fe/H]). Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.

@@

>>>>

%
% 
%
\textbf{Not quite sure if onez models should be its own section:} One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models. This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars. Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g. \cite{FinlatorDave2008,Bouche2010}). The assumptions that go into these models vary dramatically with complexity. Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e. ignoring stellar lifetimes) or that all metals mix instantly and homogenously. More complex models account for individual stellar lifetimes (to some degree), or may try and account for some aspects of inhomogenous mixing by constructing mulit-zone models that may separate a galaxy in radial bins (with or without mixing between bins), may account for a hot and cold component separately, with mixing between the two, or account for separate ISM and CGM components. The output of these models is typically the mean metal abundance evolution within each of the tracked components. There is generally no self-consistent perscription to account for the scatter in any abundance relationship in these models, which, when needed, is often added ad-hoc in post-processing. Regardless of the assumptions that go into these models, they are powerful tools that can be used to probe the general physical processes that govern galactic chemical evolution, and explore the vast, uncertain parameter space associated with the models that characterize these processes \citep[e.g.][]{Cote2017a}.

@@

We give a primer on how to model galactic evolution in hydrodynamics simulations. We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this dissertation. This is meant to be a broad overview of the physical processes modelled in such simulations, focusing on aspects of their implementation rather than the derivation of theory behind such processes. While important, the latter is better reserved for a much more detailed work (i.e. textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation. This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.

But first, we note that Astronomy jargon is full of idiosyncrisies. As metioned before, the word ``chemical" in the ``galactic chemical evolution" is a bit of a misnomer. This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the astrochemistry that those elements may participate in. Likewise, ``metals" refers broadly to every element except H and He. Throughout this dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars. This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that this is impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System. The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}. Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines) and O as a proxy in gas abundances (as it is the most abundant metal in the Universe and has convenient, strong emisson lines). These metallicity proxies are commonly reported in some form of normalized abundance ratio. For stellar metallicities, this is given in the form [A/B], where [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, and $N$ refers to the number of atoms of a given element (usually as [Fe/H]). Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.\footnote{And I am not going to mention issues in normalizatiion across methods of deriving these abundances... \citep[e.g.][]{KewleyEllison2008}.}

@@

\subsection{Radiative Processes and Chemistry}
\label{intro:sec:cooling}

Radiative processes are of fundamental importance in properly modelling the diversity of density, temperature, and ionization states in a multi-phase ISM. It is via radiative cooling that gas, heated by gravitational accretion onto dark matter halos, can cool, condense, become self-gravitating, and (eventually) collapse to form stars. Conversly heating, via radiative absorption or scatterings, from stellar sources within galaxies and the extragalactic sources that comprises the cosmic UV background (UVB, e.g. \cite{HM2001,HM2012,FG2011}).
